\documentclass[10pt, a4paper]{article}

% Preamble settings for a resume-like style
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{textcomp}

% Set margins for a clean resume look
\geometry{
  a4paper,
  margin=0.75in,
  headsep=0.2in,
}

% Customize section titles to mimic MD headers
\titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Customize subsection titles
\titleformat{\subsection}{\large\bfseries\raggedright}{}{0em}{}
\titlespacing{\subsection}{0pt}{8pt}{4pt}

% Define a custom list environment for skills/bullet points
\setlist[itemize]{
  leftmargin=*,
  itemsep=0pt,
  parsep=0pt,
  topsep=2pt,
}

% Prevent page numbering
\pagestyle{empty}

\begin{document}

% --- Header Section ---
\begin{center}
    \textbf{\Large Ahmed Mohammed Ali — Senior Backend Developer}
\end{center}

\vspace{-1.5mm}
\begin{center}
    \small
    \href{https://maps.app.goo.gl/YourLocation}{Baghdad, Iraq}
    $\cdot$ \href{https://wa.me/9647711455264}{+964 771 145 5264 (WhatsApp only)}
    $\cdot$ \href{mailto:ahmed.mohammed.ali9999@gmail.com}{ahmed.mohammed.ali9999@gmail.com}
    $\cdot$ \href{https://linkedin.com/in/deadboyccc}{LinkedIn}
    $\cdot$ \href{https://github.com/deadboyccc}{GitHub}
\end{center}
\hrule

% --- Professional Summary ---
\section*{Professional Summary}
Senior Backend Engineer specializing in Java and the Spring ecosystem, building cloud-native microservices using Spring Boot, Spring Security, Spring Data JPA, Spring Cloud, and reactive systems with Kotlin + Spring WebFlux. Experienced in OAuth2/OIDC (Keycloak), distributed systems, API gateways, CI/CD automation, and event-driven architectures (Kafka/RabbitMQ). Skilled in performance tuning, JVM optimization, and production-grade observability with OpenTelemetry, Prometheus, Grafana, Dynatrace, and ELK. Strong track record delivering scalable, fault-tolerant backend platforms for FinTech and enterprise systems.

% --- Technical Skills ---
\section*{Technical Skills}
\begin{description}[font=\textbf, align=left, labelwidth=2.5cm, leftmargin=\dimexpr2.5cm+\labelsep\relax]
    \item[Languages:] Java, Kotlin, JavaScript, TypeScript, C\#, C/C++, Python, SQL, DataWeave
    \item[Frameworks \& Platforms:] Spring Boot (WebFlux), Spring Security, Spring Data, Node.js, NestJS, Express.js, ASP.NET Core, MuleSoft Anypoint
    \item[Databases \& Storage:] PostgreSQL, MongoDB, MS SQL Server, MySQL, Redis, Elasticsearch
    \item[Messaging \& Integration:] RabbitMQ, Apache Kafka, ERP/FinTech Integration, gRPC, SOAP, GraphQL
    \item[Cloud \& DevOps:] Docker, Kubernetes (EKS), AWS (EC2, EKS), GCP, GitHub Actions, Jenkins, Bitbucket, Maven, Gradle
    \item[Observability \& Ops:] OpenTelemetry, Prometheus, Grafana, Kibana, Dynatrace, Anypoint Monitoring
    \item[Testing \& Quality:] JUnit, Mockito, Jest, Postman, Testcontainers, Integration \& Unit Testing
    \item[Architecture \& Practices:] Microservices, Event-Driven Architecture, DDD, Clean Architecture, SOLID, TDD
\end{description}

% --- Experience ---
\section*{Experience}

\vspace{1.5mm}
\noindent\textbf{Integration Engineer — QiCard} \hfill Baghdad, Iraq | March 2025 – Present
\begin{itemize}
    \item Completed MuleSoft Anypoint Platform Development Fundamentals (DEX401) and implemented API-led connectivity across enterprise systems.
    \item Designed, documented, and implemented System, Process, and Experience APIs (RAML) with modular reusable pipelines.
    \item Developed middleware for payment gateways and merchant services, reducing integration errors by 30\%.
    \item Built advanced DataWeave transformations tightly aligned with backend Java/Spring services.
    \item Maintained CI/CD pipelines (Maven, Jenkins, Bitbucket) with automated tests and deployment governance.
    \item Used Dynatrace for distributed tracing and APM, improving response times by 25\%.
    \item Applied Anypoint Monitoring for throughput/latency analytics during peak load.
\end{itemize}

\vspace{1.5mm}
\noindent\textbf{Backend Developer — FFC} \hfill Baghdad, Iraq (Hybrid) | February 2025 – March 2025
\begin{itemize}
    \item Built high-performance financial APIs with sub-second latency using Java, Spring Boot, and PostgreSQL.
    \item Migrated an ERP POC into a full production-grade backend architecture, automating 40\% of workflows.
    \item Implemented role-based access control, audit logs, exception tracing, and multi-layered architecture.
    \item Tuned PostgreSQL and JVM performance; introduced Redis caching and circuit-breakers.
\end{itemize}

\vspace{1.5mm}
\noindent\textbf{Backend Developer — CodeCraft} \hfill Remote | June 2024 – March 2025
\begin{itemize}
    \item Developed REST/GraphQL/SOAP APIs in Node.js + TypeScript serving 10k+ active users with 99.9\% uptime.
    \item Implemented JWT auth, RBAC, and secure login flows reducing unauthorized access incidents to almost zero.
    \item Optimized PostgreSQL/MongoDB with indexing, pooling, and caching (35\% performance improvement).
    \item Containerized microservices using Docker, deployed to AWS EKS with autoscaling (HPA).
    \item Built CI/CD pipelines with GitHub Actions and Jenkins, reducing deployment times by 50\%.
\end{itemize}

\vspace{1.5mm}
\noindent\textbf{IT Support Specialist — United Horizon} \hfill Baghdad, Iraq | Jan 2022 – Feb 2023
\begin{itemize}
    \item Resolved 200+ technical tickets monthly, improving uptime to 99.8\%.
    \item Managed Windows/Linux environments, asset tracking, and end-user training.
\end{itemize}

% --- Projects & Technical Highlights ---
\section*{Projects \& Technical Highlights}
\begin{itemize}
    \item \textbf{Kotlin + WebFlux Reactive Payments Service (NEW):} Built a fully non-blocking payment authorization microservice using Kotlin, Spring WebFlux, R2DBC, and Reactor. Implemented structured concurrency with coroutines, reactive Redis caching, and OpenTelemetry tracing. Achieved a 40\% throughput improvement over the synchronous Java version.
    \item \textbf{FinTech \& ERP Integration:} Secure, scalable backend integrating payment APIs, async messaging, and ERP pipelines handling 1,000+ transactions/min.
    \item \textbf{Cloud-native Microservices Blueprint:} Spring Boot + Node.js event-driven architecture with Kafka and scalable horizontal design.
    \item \textbf{Open Source Contributions:} Microservices templates, integration libraries, and Node.js profiling utilities.
    \item \textbf{Technical Blogging:} Medium series on migrating Spring Boot monoliths to Kubernetes microservices.
\end{itemize}

% --- Education ---
\section*{Education}
\begin{itemize}
    \item \textbf{American University of Iraq, Sulaimani (AUIS)} — Full-ride scholarship (left to pursue advanced backend specialization)
    \item \textbf{Baghdad College High School} — GPA: 98/100
\end{itemize}

% --- Certifications ---
\section*{Certifications}
\begin{itemize}
    \item CS50x, CS50P, CS50W — Harvard University
    \item MuleSoft Anypoint Platform Development Fundamentals (DEX401)
    \item Additional courses (Udemy, Coursera, MIT OCW) on backend engineering and distributed systems
\end{itemize}

% --- Continuous Learning & Areas of Focus ---
\section*{Continuous Learning \& Areas of Focus}
\begin{itemize}
    \item \textbf{Spring Ecosystem:} Spring 6, Boot 3, WebFlux, DI, Jakarta EE
    \item \textbf{Data Engineering:} PostgreSQL indexing, partitioning, replication; Hibernate
    \item \textbf{Microservices:} Spring Cloud, Resilience4j, Kubernetes, GKE, Helm
    \item \textbf{Events:} Kafka Streams, Schema Registry, SAGA patterns
    \item \textbf{Security:} OAuth2/OIDC, Keycloak, JWT, gRPC
    \item \textbf{Tooling:} Maven/Gradle, Testcontainers, Kotlin
\end{itemize}

% --- Interests ---
\section*{Interests \& Advocacy}
\begin{itemize}
    \item TDD, clean code, DDD, competitive programming
    \item Mental health, sustainability, animal rights
    \item Physics, mathematics, hiking, meditation, esports
\end{itemize}

\vspace{4mm}
\begin{center}
    References available upon request.
\end{center}

\end{document}
