\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\begin{document}

% Header
\begin{center}
  {\LARGE \textbf{Ahmed Mohammed Ali}}\\[0.2cm]
  +964 771 145 5264 (WhatsApp only) $\vert$ \href{mailto:ahmed.mohammed.ali9999@gmail.com}{ahmed.mohammed.ali9999@gmail.com} $\vert$ Baghdad, Iraq\\
  \href{https://www.linkedin.com/in/deadboyccc}{linkedin.com/in/deadboyccc} $\vert$ \href{https://github.com/deadboyccc}{github.com/deadboyccc}
\end{center}

% Professional Summary
\section*{Professional Summary}
Well-rounded Backend Developer with 6+ years of experience designing, integrating, and optimizing secure, scalable APIs (REST, SOAP, GraphQL, gRPC) and distributed systems. Proven expertise in Node.js, Spring Framework, ASP.NET Core, and MuleSoft Anypoint Platform. Strong foundation in low-level programming and system internals, with a focus on microservices architecture, financial system integration, and security within FinTech and ERP domains. Deep interest in DevOps practices, cloud infrastructure (AWS), and performance optimization. Seeking remote or relocation opportunities to contribute to high-impact global teams and drive robust, maintainable engineering solutions.

% Experience
\section*{Experience}
\subsection*{QiCard, Baghdad, Iraq}
\textbf{Integration Engineer} \hfill March 2025 -- Present (On-site)\\
\begin{itemize}\itemsep0pt
  \item Completed MuleSoft Anypoint Platform Development Fundamentals (DEX401) and leveraged API-led connectivity to orchestrate seamless enterprise integrations.
  \item Designed, documented, and implemented System, Process, and Experience APIs using RAML—ensuring modularity, reusability, and consistent data schemas.
  \item Developed middleware layers for payment gateways, merchant services, and internal systems; improved data flow consistency and reduced integration errors by 30\%.
  \item Authored complex DataWeave scripts and analyzed Java codebases to align integration flows with backend business logic.
  \item Implemented advanced error-handling patterns, connector configurations, and policies; maintained CI/CD pipelines with Maven, Bitbucket, and Jenkins for automated deployments.
  \item Collaborated with cross-regional teams (Egypt, UAE) to coordinate deployments, enforce governance, and maintain quality standards across environments.
  \item Utilized Dynatrace for APM and distributed tracing—monitoring CPU, JVM, heap, and thread metrics; optimized microservices performance, reducing average response time by 25\%.
  \item Employed Anypoint Monitoring and Analytics to track throughput and latency under peak loads; recommended infrastructure scaling and load-balancing strategies.
  \item Actively contributed to sprint planning and backlog refinement within an Agile framework, ensuring timely delivery of integration features.
\end{itemize}

\subsection*{FFC, Baghdad, Iraq}
\textbf{Backend Developer} \hfill February 2025 -- March 2025 (Hybrid)\\
\begin{itemize}\itemsep0pt
  \item Integrated core financial business logic into a real-time mobile fintech application, enabling secure user transactions with sub-second latency.
  \item Led the transition from an ERP proof-of-concept to a production-grade API architecture—delivering automated workflows and reducing manual processes by 40\%.
  \item Architected a multi-layered, decoupled backend with robust audit logging, exception traceability, and role-based access control (RBAC), enhancing system reliability and compliance.
  \item Tuned PostgreSQL queries, implemented Redis caching strategies, and applied circuit-breaker patterns to ensure high availability and data integrity.
  \item Conducted performance profiling (JVM, SQL) and implemented optimizations that improved overall API throughput by 20\%.
\end{itemize}

\subsection*{CodeCraft, Remote}
\textbf{Backend Developer} \hfill June 2024 -- March 2025 (Part-time)\\
\begin{itemize}\itemsep0pt
  \item Designed, developed, and maintained production-grade REST, GraphQL, and SOAP APIs using Node.js, Express.js, and TypeScript—serving 10k+ active users with 99.9\% uptime.
  \item Implemented JWT-based authentication, RBAC, and secure login flows; reduced unauthorized access incidents to near zero.
  \item Optimized MongoDB and PostgreSQL databases by refining indexing strategies, connection pooling, and caching with Mongoose and Sequelize—improving average query times by 35\%.
  \item Containerized microservices with Docker, deployed to AWS (EC2, EKS), and configured Kubernetes horizontal pod autoscaling—enabling seamless scaling under variable loads.
  \item Configured CI/CD pipelines using GitHub Actions and Jenkins for regression-free deployments; achieved a 50\% reduction in deployment time.
  \item Applied Domain-Driven Design (DDD) and Clean Architecture principles to decouple business logic, improving code maintainability and facilitating rapid feature additions.
  \item Leveraged low-level networking knowledge (C++) to optimize request handling and reduce latency under high-concurrency scenarios.
  \item Wrote comprehensive test suites with Jest and Postman for unit and integration testing, ensuring 95\% code coverage and minimal production bugs.
\end{itemize}

\subsection*{United Horizon, Baghdad, Iraq}
\textbf{IT Support Specialist} \hfill January 2022 -- February 2023 (On-site)\\
\begin{itemize}\itemsep0pt
  \item Provided Tier 1 and Tier 2 technical support for hardware, software, and networking issues—resolving 200+ tickets per month and improving system uptime to 99.8\%.
  \item Managed installation, configuration, and maintenance of Windows and Linux server environments, ensuring high availability for critical internal services.
  \item Created and maintained an IT asset inventory system, streamlining hardware tracking and reducing resource allocation errors by 25\%.
  \item Trained end users on system best practices and security policies, leading to a 40\% decrease in recurring support requests.
\end{itemize}

% Skills
\section*{Skills}
\begin{tabular}{p{3cm} p{11cm}}
{\textbf{Languages\& Tech}} & JavaScript, TypeScript, Java, C\#, C/C++, Python, SQL, DataWeave\\
{\textbf{Frameworks\& Platforms}} & Node.js, NestJS, Express.js, Spring Boot, ASP.NET Core, MuleSoft Anypoint Platform\\
{\textbf{APIs \& Integration}} & RESTful APIs, SOAP, GraphQL, gRPC, API-Led Connectivity, RabbitMQ, Apache Kafka, ERP \& FinTech Integration\\
{\textbf{Databases \& ORM}} & PostgreSQL, MongoDB, Microsoft SQL Server, Redis, Mongoose, Sequelize, Hibernate, Entity Framework Core\\
{\textbf{DevOps \& Cloud}} & Docker, Kubernetes, AWS (EC2, EKS), Git, GitHub, Bitbucket, Jenkins, Maven, Nginx, PM2, CI/CD Pipelines\\
{\textbf{Architectural Patterns}} & Microservices Architecture, Event-Driven Architecture, Domain-Driven Design, Clean Architecture, SOLID Principles, TDD, Dependency Injection, Reactive Programming\\
{\textbf{Monitoring \& Analytics}} & Dynatrace, Anypoint Monitoring, APM, Logging \& Alerting, Distributed Tracing\\
{\textbf{Testing}} & JUnit, Jest, Postman, Integration Testing, Unit Testing, Test Containers
\end{tabular}

% Education
\section*{Education}
\textbf{American University of Iraq, Sulaimani (AUIS)}\\
Full-Ride Scholarship Recipient; voluntarily left to pursue advanced, self-paced learning aligned with professional goals.

\textbf{Baghdad College High School}\\
High School Diploma, GPA: 98/100

\textbf{Additional Learning \& Certifications}\\
CS50x, CS50P, CS50W (Harvard University); MuleSoft Anypoint Platform Dev Fundamentals (DEX401); Various Udemy, Coursera, edX, and MIT OCW courses covering backend development, distributed systems, and system design.

% Projects & Technical Highlights
\section*{Projects \& Technical Highlights}
\begin{itemize}\itemsep0pt
  \item \textbf{Early Start \& Passion}: Began programming in BASIC at age 13; built foundational skills in logic and problem-solving through high-school CS coursework.
  \item \textbf{FinTech \& ERP Integration}: Delivered secure, scalable backend systems integrating payment APIs, asynchronous messaging (RabbitMQ), and ERP data pipelines—processing 1,000+ transactions per minute with end-to-end encryption and audit trails.
  \item \textbf{Open Source Contributions}: Maintained and contributed to backend-focused GitHub repositories, including microservices templates, integration libraries, and performance monitoring tools. Sample projects: a TypeScript-based GraphQL gateway and a performance profiling utility for Node.js microservices.
  \item \textbf{System Architecture Focus}: Designed a cloud-native microservices reference architecture (Node.js + Spring Boot) for a mock e-commerce platform—showcasing event-driven order processing and horizontal scaling. Published a Medium series on migrating monolithic Java apps to Kubernetes microservices, covering CI/CD, observability, and cost optimization.
\end{itemize}

% References
\vfill
\noindent\textit{References available upon request.}

\end{document}
